### 2015-05-08 fundamentals/impl.tex
Reviewer 2: page 18: SWUs please give a complete list of acronyms: here Separate Work Units

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
attach such constraints to its bids.

@@

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
\Class{Composition}), in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

>>>>

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment 
in \glspl{SWU}. It attaches such constraints to its bids.

@@

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
\Class{Composition}), in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the \gls{SWU} and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.
